\begin{thebibliography}{9}
\addtolength{\leftmargin}{0.2in}
\setlength{\itemindent}{-0.2in}

\bibitem[1]{apostol} Apostol, Tom M. \emph{Calculus}. Reverté Ediciones. México. 1999.
\bibitem[2]{avram} Avram, F., Chan, T., Usabel, M. \emph{On the valuation of constant barrier options under spectrally one-sided exponential Lévy models and Carr's aproximation for American puts}. Stochast. Process. Appl. 100, 75-107.
\bibitem[3]{bartle} Bartle, Robert G. \emph{The Elements of Real Analysis}. John Wiley \& Sons. Londres. 1964.
\bibitem[4]{billingsley} Billingsley, Patrick. \emph{Convergence of Probability Measures}. John Wiley \& Sons. 2da edición. Londres. 1999
\bibitem[5]{doob} Doob, J. L., \emph{Stochastic Processes}, Wiley, Ser. Probab. Math. Stat. New York. 1953.
\bibitem[6]{gut} Gut, Allan, \emph{Probability: A Graduate Course}, Springer Texts in Statistics. New York. 2005.
\bibitem[7]{jacodprotter} Jacod, Jean; Protter, Philip E. \emph{Probability essentials}. Universitext, Springer. 2da edición. New York. 2000.
\bibitem[8]{kyprianou} Kyprianou, Andreas E. \emph{A Hands-on Approach to Optimal Stopping}, 6th School of Probability and Stochastic Process. México. 2009.
\bibitem[9]{kyprianou2} Kyprianou, Andreas E. \emph{Fluctuations of Lévy Processes with Applications: Introductory Lectures}. Universitext, Springer. 2da edición. 2013.
\bibitem[10]{marczyg} Marcinkiewicz, J.; Zygmund A. \emph{Sur les fonctions indépendantes}, Fundam. Math. 29 (1937), 309–335.
\bibitem[11]{mortersperes} Mörters, P.; Peres Y. \emph{Brownian Motion}, Cambridge University Press. 2da edición. Cambridge. 2010.
\bibitem[12]{peskirshiryaev} Peskir, Goran; Shiryaev, Albert. \emph{Optimal Stopping and Free-Boundary Problems}. Lectures in Mathematics. ETH Zürich, Springer Science \& Business Media. 2006.
\bibitem[13]{shiryaev} Shiryaev, Albert. \emph{Probability}. Graduate Text in Mathematics Vol. 95. Springer. 2da edición. New York. 1995.

\end{thebibliography}